Update Meeting: 14-06-2021

### 2021-06-18 analysis/update_meeting_14_06_2021.Rmd
wflow_publish(c("analysis/index.Rmd", "analysis/update_meeting_14_06_2021.Rmd"))

### Summary Heterogeneity between sexes.

@@

>>>>

### Summary of results

- IVW estimates report sex-specific results
- MR_meta statistics refer to the meta of both-sexes combined. 
- Sex heterogeneity column reports the p-value of the difference between the MR estimates from the two sexes.

@@

- The first table represents the results of individuals binned by average age. 
- The second table represent the results of individuals binned by time together.
- Q p-values report the difference amongst bins.
